### 2020-09-24 5_Thesis/THESIS_LaTeX/Chapters/1.tex
thesis in progress
thesis update

\begin{figure}[th]
\centering
\includegraphics[width=1.0\textwidth]{./Figures/FabricationProcess2.png}
\decoRule
\caption[Fabrication Process]{Fabrication process and characterization techniques of conductive carbon nano-wires to achieve through the dissertation.}
\label{fig:fabricationFlowChart}
\end{figure}

@@

Carbon is a versatile element capable to form a number of bonds with other elements or with itself. Furthermore, carbon orbitals have the ability to hybridize in sp1, sp2 and sp3 configurations, hence the existence of different types of allotropes, see Figure \ref{fig:carbonAllotropes}. To date, the three naturally occurring allotropes of carbon (diamond, amorphous carbon and graphite), have been joined by additional ones deriving from synthetic processes (such as graphene, carbon nanotubes, fullerenes, carbon nanohorns, nanodiamonds) [ [12]; Fig. 1].

>>>>

\begin{figure}[th]
\centering
\includegraphics[width=1.0\textwidth]{./Figures/FabricationProcess.png}
\decoRule
\caption[Fabrication Process]{Fabrication process and characterization techniques of conductive carbon nano-wires to achieve through the dissertation.}
\label{fig:fabricationFlowChart}
\end{figure}

@@

Carbon is a versatile element capable to form a number of bonds with other elements or with itself. Furthermore, carbon orbitals have the ability to hybridize in sp1, sp2 and sp3 configurations, hence the existence of different types of allotropes, see Figure \ref{fig:carbonAllotropes}. Currently, the three carbon allotropes (diamond, amorphous carbon and graphite), have been joined by additional ones deriving from synthetic processes (such as graphene, carbon nano-tubes, fullerenes, carbon nanohorns, nanodiamonds) [ [12]; Fig. 1].
